A comparative risk assesment of U.S. regional active transport using the ITHIM model

### 2016-10-05 manuscript/manuscript.tex
More edits to manuscript.

\begin{figure}[t]
  \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig4.pdf}}
    \caption{California \& New York Averted DALYs Nationwide}\label{California}
\end{figure}

@@

We used the National Household Transportation Survey \cite{NHTS} to
estimate the mean walk and cycle times for individuals that live in
metropolitan areas for each of seven states (CA, TX, NY, FL, VA, NC
and AZ) which had sufficient sample size for reasonable estimates of
age-sex specific travel-related walking and cycling means, Figure
\ref{meanMatrices}.  Of these seven states two were found to have
active transport behavior that would avert thousands of DALYs if
adopted nation-wide. Values for national disease-specific DALYs were
found using the CDC Wonder database \cite{CDCWonder}.

\begin{figure}[t]
    \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig2}}
    \caption{Change in total national DALYs for each regional
      transportation estimates.}\label{dalyFigure}
\end{figure}

\begin{figure}[t]
  \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig3.pdf}}
    \caption{Mean travel time by mode (walking/cycling) for each of
      seven states National means are displayed on the right.}\label{meanMatrices}
\end{figure}

@@

%% \subsection{Road Injuries}

%% \textit{ We chose to model road injuries in a more simplifed manner
%%   than the authors of ITHIM.  The original ITHIM requires information
%%   about the transportational infrastructure that cannot be accurately
%%   modeled on a regional level, and is more well-suited to say a
%%   collection of counties as a case study. \cite{maizlish2013} We use
%%   the overall percent of travel by walking and road fatalities per
%%   U.S. metropolitan area to estimate road fatalaties in
%%   U.S. metropolitan areas given the percent of travel by
%%   walking. \cite{UWTechReport}}

>>>>

\begin{figure}[t]
    \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig2}}
    \caption{}\label{dalyFigure}
\end{figure}

\begin{figure}[t]
  \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig3.pdf}}
    \caption{Mean travel time by mode (walking/cycling) for each of
      seven states.  National means are displayed on the
      right.}\label{meanMatrices}
\end{figure}

\begin{figure}[t]
  \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig4.pdf}}
    \caption{}\label{California}
\end{figure}

@@

We used the National Household Transportation Survey to estimate the
mean walk and cycle times for individuals that live in metropolitan
areas for each of seven states (CA, TX, NY, FL, VA, NC and AZ)
\cite{NHTS}.  These states were selected becaused they had sufficient
sample size for reasonable estimates of age-sex specific
travel-related walking and cycling means, Figure \ref{meanMatrices}.

Of these seven states one was found to show active transport behavior
that, if adopted nation-wide, would avert 75-100,000 DALYs overall.
Values for national disease-specific DALYs were found using the CDC
Wonder database \cite{CDCWonder}.  California stood out among the
estimates for national DALYs averted.  Most of the decrease in DALYs
is due to prevention of dementia in the oldest age group, $80+$ years
old.  California exhibits much greater walking means in this age group
than the national average.  We also see prevention of depression and
diabetes in the middle age groups due to increased active transport
time.

@@

%% \subsection{Road Injuries}
%% \textit{ We chose to model road injuries in a more simplifed manner
%%   than the authors of ITHIM.  The original ITHIM requires information
%%   about the transportational infrastructure that cannot be accurately
%%   modeled on a regional level, and is more well-suited to say a
%%   collection of counties as a case study. \cite{maizlish2013} We use
%%   the overall percent of travel by walking and road fatalities per
%%   U.S. metropolitan area to estimate road fatalaties in
%%   U.S. metropolitan areas given the percent of travel by
%%   walking. \cite{UWTechReport}}
